Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-07-08 article.tex
small changes

\begin{figure}
\centering
\subfigure[Raw signal]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
\subfigure[Low-pass filter $f_1$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}
\subfigure[High-pass filter $g$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}\\
\subfigure[Hard-threshold filter $h$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}
\subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:weight_curve}}
\caption{Signal processing pipeline for extracting peaks from the raw fluorescence data.}
\label{fig:filtered-signal}
\end{figure}

@@

\begin{figure}[t]
\centering
\subfigure[ROC curves]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
\subfigure[Precision-recall curves]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
\caption{ROC (left) and PR (right) curves on \textit{normal-2} for the compared methods. Areas under the curves are reported in the legend.}
%% The weighted average of partial correlation matrix, winning approach
         %% of the challenge, yields better than AUROC and AUPRC than all
         %% other state-of-the-art methods. (parameters: $\tau=0.11$ except for
         %% averaged partial correlation method, partial correlation used
         %% filter $f_1$). Area under the curves are given between $()$
         %% for the corresponding methods.
%}
\label{fig:curves}
\end{figure}

@@

Filters $f_1$ and $f_2$ display similar performances and thus were given similar
weights (i.e., resp. $0.383$ and $0.345$). These weights were chosen equal as the weights selected for the simplified method. In contrast, filters $f_3$
and $f_4$ turn out to be individually less competitive and were therefore given
smaller importance in the weighted average (i.e., resp. $0.004$ and $0.268$). Yet, as further shown in
Section~\ref{sapp:results}, combining all $4$ filters proves to slightly
improve performance with respect to using $f_1$ and $f_2$ only.

>>>>

\begin{figure}
\centering
\subfigure[Raw signal]{\includegraphics[width=0.3\textwidth]{original_curve.pdf} \label{fig:original_curve}}
\subfigure[Low-pass filter $f_1$]{\includegraphics[width=0.3\textwidth]{filter_curve.pdf} \label{fig:lp_curve}}
\subfigure[High-pass filter $g$]{\includegraphics[width=0.3\textwidth]{diff_curve.pdf} \label{fig:hp_curve}}\\
\subfigure[Hard-threshold filter $h$]{\includegraphics[width=0.3\textwidth]{threshold_curve.pdf} \label{fig:threshold_curve}}
\subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{weights_curve.pdf} \label{fig:weight_curve}}
\caption{Signal processing pipeline for extracting peaks from the raw fluorescence data.}
\label{fig:filtered-signal}
\end{figure}

@@

\begin{figure}[t]
\centering
\subfigure[ROC curves]{\includegraphics[width=0.45\textwidth]{curve_roc} \label{fig:roc_curve}}
\subfigure[Precision-recall curves]{\includegraphics[width=0.45\textwidth]{curve_pr} \label{fig:pr_curve}}
\caption{ROC (left) and PR (right) curves on \textit{normal-2} for the compared methods. Areas under the curves are reported in the legend.}
%% The weighted average of partial correlation matrix, winning approach
         %% of the challenge, yields better than AUROC and AUPRC than all
         %% other state-of-the-art methods. (parameters: $\tau=0.11$ except for
         %% averaged partial correlation method, partial correlation used
         %% filter $f_1$). Area under the curves are given between $()$
         %% for the corresponding methods.
%}
\label{fig:curves}
\end{figure}

@@

Filters $f_1$ and $f_2$ display similar performances and thus were given similar
weights (i.e., resp. $0.383$ and $0.345$). These weights were chosen equal to the weights selected for the simplified method. In contrast, filters $f_3$
and $f_4$ turn out to be individually less competitive and were therefore given
smaller importance in the weighted average (i.e., resp. $0.004$ and $0.268$). Yet, as further shown in
Section~\ref{sapp:results}, combining all $4$ filters proves to slightly
improve performance with respect to using $f_1$ and $f_2$ only.
